Baseline centering problem

### 2018-12-19 paper/tangotd.tex

The Newton update is
\begin{equation}
Z\gets (1+\eta)Z-\eta Z^2+\eta \gamma ZPZ
\end{equation}
which after applying to $\1_{s_1}$ on the left yields
\begin{multline}
Z(s_1,s_2)\gets (1+\eta)Z(s_1,s_2)-\eta \E_{s_3\sim \rho}
Z(s_1,s_3)Z(s_3,s_2)\,+\\\eta \gamma \E_{s_3\sim\rho, s'_3\sim P(s'_3|s_3)}
Z(s_1,s_3)Z(s'_3,s_2)
\end{multline}
and we should find a way to initialize $Z$ so that $Z\approx \Id$ at time
$0$.

>>>>

The Newton update is
\begin{equation}
Z\gets (1+\eta)Z-\eta Z^2+\eta \gamma ZPZ
\end{equation}
which after applying to $\1_{s_1}$ on the left yields
\begin{multline}
Z(s_1,s_2)\gets (1+\eta)Z(s_1,s_2)-\eta \E_{s_3\sim \rho}
Z(s_1,s_3)Z(s_3,s_2)\,+\\\eta \gamma \E_{s_3\sim\rho, s'_3\sim P(s'_3|s_3)}
Z(s_1,s_3)Z(s'_3,s_2)
\end{multline}
and we should find a way to initialize $Z$ so that $Z\approx \Id$ at time
$0$ ($Z(s,s)=1/\rho(s)$, although starting with $Z(s,s)=1$ should be
enough). In the end this Newton equation alone might be sufficient to
encompass the left and right Bellman. It does not rely on test functions,
but the smoothing is implicit via the model used for $Z(s_1,s_2)$.
